Environment modeling in \tool

### 2022-05-02 paper.tex
pass section 2

In the context of symbolic execution compiler, we can choose between modeling the environment in the source language level or in the target language level. \tool translates LLVM-IR (compiled from C programs) into backend C++ programs. As we mentioned before, we choose to model the environment in the file system level like KLEE, so we can either directly porting KLEE's file system (written in C) or develops our own internal file system as backend C++ runtime library. We will discuss this two implementations in detail and compare their advantage and disadvantage.
\paragraph*{Porting KLEE's file system}
KLEE develops a POSIX-like symbolic file system on top of the native file system in order to alleviate side effects caused by external calls and prevent interference across execution paths. The symbolic file system is written purely in C and can be linked with the user program to be analyzed. This file system can be easily modified and extended without mangling
 with the internal details. In fact, by implementing the entire symbolic file system in the C level, it can be ported to other well-formed symbolic engine with no modification. We can directly port KLEE's file system into our model with little effort.\par
 KLEE's file system is a hybrid approach, it contains both symbolic files and concrete files. It maintains symbolic meta data like offset and open flags for both symbolic and concrete files. For symbolic files, it will allocated a char array buffer upon creation to store its symbolic content and a symbolic stat struct to store its symbolic status. For concrete file, it will records its actual file descriptor upon open for future references.\par

@@

    f$\rightarrow$off += actual_count;
    return actual_count;
  }
}
\end{lstlisting}
\vspace{-1em}
%\caption{The generated code of the LLVM \texttt{power} function by \tool.
\end{subfigure}
\caption{
  Upper: The sketch of KLEE file system's write() }
\vspace{-0.3in}
\label{fig:example}
\end{figure}

 Each system call interacting with the file system will check whether the file is a symbolic file first as shown in Figure \ref{fig:example}. If the file is symbolic, it will use memcpy or other memory modification function to manipulate the char array buffer storing the actual symbolic content. If the file is concrete, it will uses the stored actual file descriptor to access the real file stored on disk. KLEE's file system stores offset for both symbolic and concrete files and uses pread() and pwrite() to accessing concrete files using the managed offset to prevent interference between paths.\par
 KLEE's file system is a simple and straightforward approach to model the environment in the source language level, it can switch between invoke native system call and access internal symbolic file system. We directly reuse it as the source language implementation of the file system.

@@

Besides modeling the file system in the source language level, we can also develop a symbolic file system in the target language as runtime libraries. By embedding the file system inside the state, file system operations can be viewed as operating on the file system object.

@@

With knowledge of the detailed internal memory model and state representation, we can write more optimized code of each file system operations for different engines.\par
Besides directly writing the file system in the target language (C++) level, we can also use meta programming and code generation techniques to generate the file system library in LMS.

@@

Implementing the file system in the source language level has the advantages of portability and flexibility. It can be ported to a completely different framework with little effort without the need to mangle with the underlying internal engine details. We can also switch more flexibly  between different designs. For example, we can enable symbolic filenames simply by making the filename symbolic and requires no modification in the file system, the underlying symbolic engine will deal with the state forking as it analyzes our file system code along with the user code after linking. However, in order to achieve the same goal in the target language level implementation, we will need to understand the internal control representation (direct style or CPS-style) and modify the open system call in the runtime library to handle the possible forking of states accordingly.\par
Although implementing file system in the source language is portable and flexible, it lacks efficiency and performance. As a example, we can look at the write() system call implementation sketch in Figure \ref{fig:example}. All the control flow structure (if-else statement, function call) will be compiled into the corresponding backend control representation, increasing the performance overhead. Furthermore, if we are accessing a symbolic file, write() will invoke memcpy function, triggering a loop to copy the memory. Inside each loop iterations, memcpy will first use lookup to read one byte from the src address, and then write the byte into the dest address. Because the file system is implemented on the source language level, each memory read and write will be compiled into lookup and update of internal memory model and invoke the corresponding runtime library, causing significant performance degrading. The source language level file system always executes on top of the underlying control and memory representation, resulting multiple levels of indirection and slow down the overall performance. We can see more concrete examples in the benchmark in section \ref{evaluation}.

@@

This section shows the evaluation benchmarks of running Coreutils programs on \tool with both two file systems and KLEE. \tool has two file system implementations, one written in the source language level (directly porting KLEE's POSIX filesystem), one written in the target language level as runtime library. We also run the same program on KLEE to compare the performance with \tool. Because we directly port KLEE's file system as the source level implementation, comparison between \tool with KLEE's POSIX file system and KLEE is fair and can measure the efficiency of this two symbolic execution engines. We will use \tool/POSIX to represent our framework with KLEE's filesystem implementation, \tool/FS to represent our framework with the internal target language level file system implementation and KLEE/POSIX to represent KLEE with its file system. We choose echo from Coreutils programs for testing and we perform all the experiment on the Intel(R) Xeon(R) Platinum 8168 CPU @ 2.70GHz 192 core cpu on server bigdata2.cs.purdue.edu. We use g++ with -O3 to compile the generated C++ code as mentioned in section \ref{coreutilstests}. The running time is shown in Table \ref{tab:coreutils_benchmarks_echo} and Figure \ref{fig:speedup}.\par

>>>>

In symbolic execution compiler, we can choose between modeling the environment at the source language level or the target language level. \tool translates LLVM-IR (compiled from C programs) into backend C++ programs. As we mentioned before, we choose to model the environment at the file system level like KLEE, so we can either directly reuse KLEE's file system (written in C) or develops our internal file system as a backend C++ runtime library. We will discuss these two implementations in detail and compare their advantage and disadvantage.
\paragraph*{Reusing KLEE's file system}
KLEE develops a POSIX-like symbolic file system on top of the native file system to alleviate side effects caused by external calls and prevent interference across execution paths. The symbolic file system is written purely in C and can be linked with the user program to be analyzed. This file system can be easily modified and extended without mangling
 the internal engine details. It can be ported to other well-formed symbolic engines with no modification. With little effort, we can directly use KLEE's file system in our model.\par
 KLEE's file system is a hybrid approach. It contains both symbolic files and concrete files. It maintains symbolic metadata like offset and open flags for symbolic and concrete files. For symbolic files, it will allocate a char array buffer upon creation to store its symbolic content and a symbolic stat struct to store its symbolic status. For concrete files, it will record its actual file descriptor upon opening for future references.\par

@@

    f$\rightarrow$off += actual_count;
    return actual_count;
  }
}
\end{lstlisting}
\vspace{-1em}
%\caption{The generated code of the LLVM \texttt{power} function by \tool.
\end{subfigure}
\caption{The sketch of KLEE file system's write() }
\vspace{-0.3in}
\label{fig:example}
\end{figure}

Each system call interacting with the file system will check whether the file is symbolic first, as shown in Figure \ref{fig:example}. If the file is symbolic, it will use memcpy or other function to manipulate the char array buffer storing the actual symbolic content. If the file is concrete, it will use the stored actual file descriptor to access the real file stored on disk. KLEE's file system stores offset for both symbolic and concrete files and use pread() and pwrite() to access concrete files using the managed offset to prevent interference between paths.\par
KLEE's file system is a straightforward approach to modeling the environment at the source language level. It switches between invoking native system calls and accessing the internal symbolic file system. We directly reuse it as the source language implementation of the file system.

@@

 Besides modeling the file system at the source language level, we can also develop a symbolic file system in the target language as runtime libraries. By embedding the file system inside the state, file system operations can be viewed as operating on the file system object.

@@

Knowing the detailed internal memory model and state representation, we can write more optimized code for each file system operation for different backend engines.\par
Besides directly writing the file system at the target language (C++) level, we can also use meta-programming and code generation techniques to generate the file system library in LMS.

@@

Implementing the file system at the source language level has the advantages of portability and flexibility. It can be ported to a completely different framework with little effort without the need to mangle with the underlying internal engine details. We can also switch more flexibly between different designs. For example, we can enable symbolic filenames simply by making the filename symbolic, and no modification in the file system is required. The underlying symbolic engine will deal with the state forking as it analyzes our file system code with the user code after linking. However, to achieve the same goal in the target language level implementation, we will need to understand the internal control representation (direct style or CPS-style) and modify the open system call in the runtime library to handle the possible forking of states accordingly.\par
Although implementing file system in the source language is portable and flexible, it lacks efficiency and performance. The file system always executes on top of the underlying control and memory representation, resulting in multiple levels of indirection and slowing down the overall performance. As an example, we can look at the write() system call implementation sketch in Figure \ref{fig:example}. All the control flow structures (if-else statement, function call) will be compiled into the corresponding backend control representation, increasing the performance overhead. Furthermore, if we access a symbolic file, write() will invoke the memcpy function, triggering a loop to copy the memory. Inside each loop iteration, memcpy will first read one byte from the src address and then write the byte into the dest address. Because the file system is implemented on the source language level, each memory read and write will be compiled into lookup and update of the internal memory model and invoke the corresponding runtime library, causing significant performance degrading. We can see some evaluations validating this observation in section \ref{evaluation}.

@@

This section shows the evaluation benchmarks of running Coreutils programs on \tool with both two file systems and KLEE. \tool has two file system implementations, one written in the source language level (directly porting KLEE's POSIX filesystem), one written in the target language level as runtime library. We also run the same program on KLEE to compare the performance with \tool. Because we directly reuse KLEE's file system as the source level implementation, comparison between \tool with KLEE's POSIX file system and KLEE is fair and can measure the efficiency of this two symbolic execution engines. We will use \tool/POSIX to represent our framework with KLEE's filesystem implementation, \tool/FS to represent our framework with the internal target language level file system implementation and KLEE/POSIX to represent KLEE with its file system. We choose echo from Coreutils programs for testing and we perform all the experiment on the Intel(R) Xeon(R) Platinum 8168 CPU @ 2.70GHz 192 core cpu on server bigdata2.cs.purdue.edu. We use g++ with -O3 to compile the generated C++ code as mentioned in section \ref{coreutilstests}. The running time is shown in Table \ref{tab:coreutils_benchmarks_echo} and Figure \ref{fig:speedup}.\par
